### 2015-02-28 paper_20_sdo.tex
minor changes around the acronym SDO uploaded new output PDF file

\section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
A \textit{Software Development Organization} is any organization or subset of an organization that is responsible
for the creation, deployment, and maintenance of software.  Many times a software development organization
is a company that produces software.  Other times, a software development organization is contained
within the Information Technology department of a larger organization. Some of the job roles
with an SDO are: software engineer, system administrator, software quality analyst,
programmer, database administrator, and documentation specialist.

>>>>

\section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
A \textit{Software Development Organization (SDO)} is any organization or subset of an organization that is responsible
for the creation, deployment, and maintenance of software.  Many times a software development organization
is a company that produces software.  Other times, a software development organization is contained
within the Information Technology department of a larger organization. Some of the job roles
with an SDO are: software engineer, system administrator, software quality analyst,
programmer, database administrator, and documentation specialist.

### 2015-02-28 paper_30_measure.tex
minor changes around the acronym SDO uploaded new output PDF file

        \subsubsection{RESULT INDICATORS (RI) FOR SDO}
            \textit{Result Indicators} are performance 
            measures that summarize activity.  All financial performance
            measures are result indicators.  Result indicators
            are measured on a timely basis (daily, weekly, monthly)
            and are the result of more than one activity.  They do not
            tell staff what needs to be done to improve the RI. For
            an SDO, some possible RIs are seen in Table \ref{tab:RI}.

@@

        \subsubsection{KEY RESULT INDICATOR (KRI) FOR SDO}
            \textit{Key Result Indicators} are measures of multiple
            activities that give a clear picture of whether the
            organization is traveling in the right direction.  Unfortunately,
            KRIs are commonly mistaken for KPIs \cite{parmenter2010}.  KRIs
            do not tell an organization what is needed to improve the 
            results.  KRIs are highly benefical for high-level management
            and not necessarily beneficial for staff working directly on 
            the software.  For
            an SDO, some possible KRIs are seen in Table \ref{tab:KRI}.

@@

        \subsubsection{PERFORMANCE INDICATOR (PI) FOR SDO}
            \textit{Performance Indicators} are nonfinancial performance measures
            that help a team align themselves with the organizations 
            strategy.  These are important to the organizations success, but
            they are not the key measures that will lead to drastic improvement.  They are specifically tied to a team and all staff understand
            what actions need to be taken to improve the PI.
            For an SDO, some possible PIs are seen in Table \ref{tab:PI}.

@@

        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR SDO}
            \textit{Key Performance Indicators} are performance measures
            focusing on critical aspects for current and future organizational
            success.  Notice, KPIs are not focused on historical performance,
            and they clearly indicate how to drastically increase performance.
            KPIs allow a team to monitor current performance and 
            quickly take action to correct future performance.
            KPIs cover a shorter time frame than KRIs.
            KPIs consist of the following 7 characteristics \cite{parmenter2010}.
            \begin{enumerate}
                \item Not financial
                \item Measured frequently (hourly, daily, weekly)
                \item Acted on by CEO\footnote{Chief Executive Officer} 
                    and/or senior management
                \item Clearly indicate the action required
                \item Tie responsibility to a particular team
                \item Have a significant impact
                \item Encourage appropriate action
            \end{enumerate}

>>>>

        \subsubsection{RESULT INDICATORS (RI) FOR AN SDO}
            \textit{Result Indicators} are performance 
            measures that summarize activity.  All financial performance
            measures are result indicators.  Result indicators
            are measured on a timely basis (daily, weekly, monthly)
            and are the result of more than one activity.  They do not
            tell staff what needs to be done to improve the RI. For
            an SDO, some possible RIs are seen in Table \ref{tab:RI}.

@@

        \subsubsection{KEY RESULT INDICATOR (KRI) FOR AN SDO}
            \textit{Key Result Indicators} are measures of multiple
            activities that give a clear picture of whether the
            organization is traveling in the right direction.  Unfortunately,
            KRIs are commonly mistaken for KPIs \cite{parmenter2010}.  KRIs
            do not tell an organization what is needed to improve the 
            results.  KRIs are highly benefical for high-level management
            and not necessarily beneficial for staff working directly on 
            the software.  For
            an SDO, some possible KRIs are seen in Table \ref{tab:KRI}.

@@

        \subsubsection{PERFORMANCE INDICATOR (PI) FOR AN SDO}
            \textit{Performance Indicators} are nonfinancial performance measures
            that help a team align themselves with the organizations 
            strategy.  These are important to the organizations success, but
            they are not the key measures that will lead to drastic improvement.  They are specifically tied to a team and all staff understand
            what actions need to be taken to improve the PI.
            For an SDO, some possible PIs are seen in Table \ref{tab:PI}.

@@

        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR AN SDO}
            \textit{Key Performance Indicators} are performance measures
            focusing on critical aspects for current and future organizational
            success.  Notice, KPIs are not focused on historical performance,
            and they clearly indicate how to drastically increase performance.
            KPIs allow a team to monitor current performance and 
            quickly take action to correct future performance.
            KPIs cover a shorter time frame than KRIs.
            KPIs consist of the following 7 characteristics \cite{parmenter2010}.
            \begin{enumerate}
                \item Not financial
                \item Measured frequently (hourly, daily, weekly)
                \item Acted on by CEO\footnote{Chief Executive Officer} 
                    and/or senior management
                \item Clearly indicate the action required
                \item Tie responsibility to a particular team
                \item Have a significant impact
                \item Encourage appropriate action
            \end{enumerate}

### 2015-02-28 paper_40_cri.tex
minor changes around the acronym SDO uploaded new output PDF file

    Software development organizations struggle to measure overall performance.  
    The Cumulative Result Indicator (CRI) is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following 5 
    elements, which are actually KRIs,
    for a software development organization.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  CRI is made to be easily 
    expandable to other elements if desired.

@@

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            All the new features and great quality do not matter if the software is not available.  Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, an SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline to data needed to properly
            calculate an SLA and the data needed to calculate the CRI score for availability.

>>>>

    Software development organizations struggle to measure overall performance.  
    The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following 5 
    elements, which are actually KRIs,
    for a software development organization.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  CRI is made to be easily 
    expandable to other elements if desired.

@@

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            All the new features and great quality do not matter if the software is not available.  Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, the SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline to data needed to properly
            calculate an SLA and the data needed to calculate the CRI score for availability.
